Paper Figures and Text

### 2024-03-18 Fish Data Analysis/Paper_Figures.qmd
Changed graph text, removed parallax figure

speed_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=max(Speed_Mean_Val-Speed_SD_Val,0), ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,6)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

speed_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,6)+
  stat_compare_means(comparisons = my_comparisons, label.y = c(5.5), label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

Parallax

```{r}
para_vals <- read.csv("Data/Parallax_Distances.csv") %>% mutate(BLs = Distance / 200)

breaks <- c("0.1")

para_plot <- ggplot(para_vals, aes(X, Y, z = BLs))+
  geom_contour_filled(bins = 5)+
  scale_fill_viridis_d("Projection Error (BL)", 
                       labels = c("< 0.1", "0.1 - 0.2", "0.2 - 0.3","0.3 - 0.4","0.4 - 0.5"))+
  theme_classic()+
  coord_fixed() +
  ylab("Vertical Distance from Principal Point (pixels)")+
  xlab("Hoizontal Distance from Principal Point (pixels)")+ 
  theme(text = element_text(size = 20))

ggsave("Paper Figures/parallax_model.png", para_plot, width = 14, height = 7)
```

>>>>

speed_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=max(Speed_Mean_Val-Speed_SD_Val,0), ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Mean Speed of Fish (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,6)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

speed_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Mean Speed of Fish (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,6)+
  stat_compare_means(comparisons = my_comparisons, label.y = c(5.5), label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@
